{\Huge Supersymmetry} \\ \vspace{5mm} Lecture notes for FYS5190/FYS9190 Supersymmetry

### 2025-10-30 mssm.tex
Fixes for lecture 30.10.25

We use these two superfield ingredients to construct all the known fermions:
\begin{itemize}
\item To represent the Standard Model leptons we introduce the superfields $l_i$ and $\bar{E}_i$ for the charged leptons ($i$ is the generation index) and $\nu_i$ for the neutrinos, and form $SU(2)_L$ doublet superfield vectors $L_i = (\nu_i, l_i)$, which contain the left-handed Weyl spinors for the particles, while $\bar{E}_i$  contain the left-handed Weyl spinors that are singlets (do not transform) under $SU(2)_L$.
\item There is an imbalance in the neutrinos in that we do not introduce the neutrino superfield $\bar{N}_i$ that through $\bar{N}_i^\dagger$ would contain right-handed neutrino spinors needed for massive Dirac neutrinos, instead leaving the neutrinos as massless Majorana particles in the MSSM.\footnote{The anti-neutrino contained in the superfield $\nu_i^\dagger$ is a right-handed Weyl-spinor consistent with experiment.}
This is a convention -- the MSSM is older than the discovery of neutrino mass -- and including $\bar{N}_i$ fields would have some interesting consequences.
%\footnote{Note that component fields in the same superfield must have the same charge under all the gauge groups, {\it i.e.}\ the scalar partner of the electron has electric charge $-e$, so it cannot be a neutrino.}
The $\bar{N}_i$ superfields and their component fields would not couple to any of the gauge fields since they are SM singlets,\footnote{They can not be colour-charged, they are singlets under $SU(2)_L$ by construction thus they have zero weak isospin $I_3$, but since they should also have zero electric charge $Q$, the hypercharge $Y$ must also be zero through the relationship $Q=\half Y+I_3$.} however, the scalar field in the superfield could be a potential dark matter candidate.
\item For quarks the situation is similar. Up-type and down-type quarks get the superfields $u_i$ and $d_i$,  forming the $SU(2)_L$ doublets $Q_i = (u_i, d_i)$, and the $SU(2)_L$  singlets $\bar{U}_i$ and $\bar{D}_i$.\footnote{Here we should really also include a colour index $a$ so that $u_i^a$ is a component in an $SU(3)_c$ triplet superfield vector. We omit these for simplicity.}
\end{itemize}

@@

@@

>>>>

We use these two superfield ingredients to construct all the known fermions:
\begin{itemize}
\item To represent the Standard Model leptons we introduce the superfields $l_i$ and $\bar{E}_i$ for the charged leptons ($i$ is the generation index) and $\nu_i$ for the neutrinos, and form $SU(2)_L$ doublet superfield vectors $L_i = (\nu_i, l_i)$, which contain the left-handed Weyl spinors for the particles, while $\bar{E}_i$  contain the left-handed Weyl spinors that are singlets (do not transform) under $SU(2)_L$.
\item There is an imbalance in the neutrinos in that we do not introduce the neutrino superfield $\bar{N}_i$ that through $\bar{N}_i^\dagger$ would contain right-handed neutrino spinors needed for massive Dirac neutrinos, instead leaving the neutrinos as massless Majorana particles in the MSSM.\footnote{The fermion contained in the superfield $\nu_i^\dagger$ is a right-handed Weyl-spinor consistent with experiment.}
This is a convention---the MSSM is older than the discovery of neutrino mass---and including $\bar{N}_i$ fields would have some interesting consequences.
%\footnote{Note that component fields in the same superfield must have the same charge under all the gauge groups, {\it i.e.}\ the scalar partner of the electron has electric charge $-e$, so it cannot be a neutrino.}
The $\bar{N}_i$ superfields and their component fields would not couple to any of the gauge fields since they are SM singlets,\footnote{They can not be colour-charged, they are singlets under $SU(2)_L$ by construction thus they have zero weak isospin $I_3$, but since they should also have zero electric charge $Q$, the hypercharge $Y$ must also be zero through the relationship $Q=\half Y+I_3$.} however, the scalar field in the superfield could be a potential dark matter candidate.
\item For quarks the situation is similar. Up-type and down-type quarks get the superfields $u_i$ and $d_i$,  forming the $SU(2)_L$ doublets $Q_i = (u_i, d_i)$, and the $SU(2)_L$  singlets $\bar{U}_i$ and $\bar{D}_i$.\footnote{Here we should really also include a colour index $a$ so that $u_i^a$ is a component in an $SU(3)_c$ triplet superfield vector. We omit these for simplicity.}
\end{itemize}

@@

% TODO: introduce more details here, including hypercharge counting (Sandvik)

@@

%TODO:  Example of  broken $U_{B-L}$ giving $\mathbb Z_2$ symmetry (Melkild), also connection to anomalies (extra neutrinos=

### 2025-10-30 poincare.tex
Fixes for lecture 30.10.25

%%%%%%%%%%%%
\section{Weyl spinors}
\label{sec:weyl}
%%%%%%%%%%%%
As we discussed at the end of Sec.~\ref{sec:Lorentz_group} there exists a two-to-one homomorphism between the  $SL(2, \mathbb{C})$ and the Lorentz group $SO^+(1,3)$. This homomorphism, with $\Lambda^\mu{}_\nu \in SO^+(1,3)$ and $M \in SL(2, \mathbb{C})$, can be explicitly given by:\footnote{The choice of sign in Eq.~(\ref{eq:MofLambda}) is the reason that this is a homomorphism, instead of an isomorphism. Each element in  $SO^+(1,3)$ can be assigned to two elements in $SL(2, \mathbb{C})$.}
\begin{eqnarray}
\Lambda^\mu{}_\nu(M) &=& \frac{1}{2}{\rm Tr}[\bar{\sigma}^\mu M \sigma_\nu M^\dagger],\label{eq:LambdaofM}\\
M(\Lambda^\mu{}_\nu) &=& \pm \frac{1}{\sqrt{\det(\Lambda^\mu{}_\nu \sigma_\mu \bar{\sigma}^\nu)}}\Lambda^\mu{}_\nu \sigma_\mu \bar{\sigma}^\nu,\label{eq:MofLambda}
\end{eqnarray}
where $\bar{\sigma}^\mu = (1, -\vec{\sigma})$ and $\sigma^\mu = (1, \vec{\sigma})$. The generators of $SO^+(1,3)$ can be shown to transform to (be proportional to) the Pauli matrices in $SL(2,\mathbb C)$:
\[ J_i=\half \sigma_i, \quad K_i=\frac{i}{2}\sigma_i. \]

@@

\begin{Exercise}[]
Use Eq.~(\ref{eq:exp_map_Lorentz}) to write out an explicit expression for a Lorentz boost in the $x$-direction with rapidity $\eta$.
\end{Exercise}
\begin{Answer} 
For a Lorentz boost in the $x$-direction all parameters are zero except $\omega_{10}=-\omega_{01}=\eta$. This gives
\begin{equation*}
\Lambda = \exp(i\omega^{10}M_{10})= \exp(i\eta K_1)=\cosh(i\eta K_1)+\sinh(i\eta K_1).
\end{equation*}
where we have used the relationship between the formal power series for the exponential and hyperbolic functions. Now the hyperbolic cosine holds the terms even in $K_1$ and hyperbolic sine the odd terms. From
\[iK_1 = - \left[\begin{matrix} 0 & 1  & 0 &  0\\  1 & 0 & 0 & 0 \\  0 & 0 & 0 & 0 \\ 0 & 0 & 0 & 0 \end{matrix}\right], \quad
(iK_1)^2 = \left[\begin{matrix} 1 & 0  & 0 &  0\\  0 & 1 & 0 & 0 \\  0 & 0 & 0 & 0 \\ 0 & 0 & 0 & 0 \end{matrix}\right], \quad
(iK_1)^3 = -\left[\begin{matrix} 0 & 1  & 0 &  0\\  1 & 0 & 0 & 0 \\  0 & 0 & 0 & 0 \\ 0 & 0 & 0 & 0 \end{matrix}\right], \]
we can write
\begin{equation*}
\Lambda = I+ (\cosh\eta-1)\left[\begin{matrix} 1 & 0  & 0 &  0\\  0 & 1 & 0 & 0 \\  0 & 0 & 0 & 0 \\ 0 & 0 & 0 & 0 \end{matrix}\right]-\sinh\eta\left[\begin{matrix} 0 & 1  & 0 &  0\\  1 & 0 & 0 & 0 \\  0 & 0 & 0 & 0 \\ 0 & 0 & 0 & 0 \end{matrix}\right]
=\left[\begin{matrix} \cosh\eta & -\sinh\eta  & 0 & 0 \\  -\sinh\eta & \cosh\eta & 0 & 0 \\  0 & 0 & 1 & 0 \\ 0 & 0 & 0 & 1 \end{matrix}\right].
\end{equation*}
Thus we are left with the standard matrix for Lorentz transformations in the $x$-direction (using rapidity).
\end{Answer}

\begin{Exercise}[]
Show that a general boost in the direction of the unit vector $\mathbf n$ with rapidity $\eta$ can be written as
\begin{equation*}
B(\eta,\mathbf n)=I+(\cosh\eta-1)(\mathbf n \cdot \mathbf K)^2-i\sinh\eta (\mathbf n \cdot \mathbf K).
\end{equation*}
\end{Exercise}

>>>>

%%%%%%%%%%%%
\section{Weyl spinors}
\label{sec:weyl}
%%%%%%%%%%%%
As we discussed at the end of Sec.~\ref{sec:Lorentz_group} there exists a two-to-one homomorphism between the  $SL(2, \mathbb{C})$ and the Lorentz group $SO^+(1,3)$. This homomorphism, with $\Lambda^\mu{}_\nu \in SO^+(1,3)$ and $M \in SL(2, \mathbb{C})$, can be explicitly given by:\footnote{The choice of sign in Eq.~(\ref{eq:MofLambda}) is the reason that this is a homomorphism, instead of an isomorphism. Each element in  $SO^+(1,3)$ can be assigned to two elements in $SL(2, \mathbb{C})$.}
\begin{eqnarray}
\Lambda^\mu{}_\nu(M) &=& \frac{1}{2}{\rm Tr}[\bar{\sigma}^\mu M \sigma_\nu M^\dagger],\label{eq:LambdaofM}\\
M(\Lambda^\mu{}_\nu) &=& \pm \frac{1}{\sqrt{\det(\Lambda^\mu{}_\nu \sigma_\mu \bar{\sigma}^\nu)}}\Lambda^\mu{}_\nu \sigma_\mu \bar{\sigma}^\nu,\label{eq:MofLambda}
\end{eqnarray}
where $\bar{\sigma}^\mu = (1, -\mathbf{\sigma})$ and $\sigma^\mu = (1, \mathbf{\sigma})$. The generators of $SO^+(1,3)$ can be shown to transform to (be proportional to) the Pauli matrices in $SL(2,\mathbb C)$:
\[ J_i=\half \sigma_i, \quad K_i=\frac{i}{2}\sigma_i. \]

@@

\begin{Exercise}[label=ex:Lorentz_explicit_x]
Use Eq.~(\ref{eq:exp_map_Lorentz}) to write out an explicit expression for a Lorentz boost in the $x$-direction with rapidity $\eta$.
\end{Exercise}
\begin{Answer} 
For a Lorentz boost in the $x$-direction all parameters are zero except $\omega_{10}=-\omega_{01}=\eta$. This gives
\begin{equation*}
\Lambda = \exp(i\omega^{10}M_{10})= \exp(i\eta K_1)=\cosh(i\eta K_1)+\sinh(i\eta K_1).
\end{equation*}
where we have used the relationship between the formal power series for the exponential and hyperbolic functions. Now the hyperbolic cosine holds the terms even in $K_1$ and hyperbolic sine the odd terms. From
\[iK_1 = - \left[\begin{matrix} 0 & 1  & 0 &  0\\  1 & 0 & 0 & 0 \\  0 & 0 & 0 & 0 \\ 0 & 0 & 0 & 0 \end{matrix}\right], \quad
(iK_1)^2 = \left[\begin{matrix} 1 & 0  & 0 &  0\\  0 & 1 & 0 & 0 \\  0 & 0 & 0 & 0 \\ 0 & 0 & 0 & 0 \end{matrix}\right], \quad
(iK_1)^3 = -\left[\begin{matrix} 0 & 1  & 0 &  0\\  1 & 0 & 0 & 0 \\  0 & 0 & 0 & 0 \\ 0 & 0 & 0 & 0 \end{matrix}\right], \]
we can write
\begin{equation*}
\Lambda = I+ (\cosh\eta-1)\left[\begin{matrix} 1 & 0  & 0 &  0\\  0 & 1 & 0 & 0 \\  0 & 0 & 0 & 0 \\ 0 & 0 & 0 & 0 \end{matrix}\right]-\sinh\eta\left[\begin{matrix} 0 & 1  & 0 &  0\\  1 & 0 & 0 & 0 \\  0 & 0 & 0 & 0 \\ 0 & 0 & 0 & 0 \end{matrix}\right]
=\left[\begin{matrix} \cosh\eta & -\sinh\eta  & 0 & 0 \\  -\sinh\eta & \cosh\eta & 0 & 0 \\  0 & 0 & 1 & 0 \\ 0 & 0 & 0 & 1 \end{matrix}\right].
\end{equation*}
Thus we are left with the standard matrix for Lorentz transformations in the $x$-direction (using rapidity).
\end{Answer}

\begin{Exercise}[]
Show that a general boost in the direction of the unit vector $\mathbf n$ with rapidity $\eta$ can be written as
\begin{equation*}
B(\eta,\mathbf n)=I-(\cosh\eta-1)(\mathbf n \cdot \mathbf K)^2+i\sinh\eta (\mathbf n \cdot \mathbf K).
\end{equation*}
\end{Exercise}
\begin{Answer}
The boost generators are given by
\begin{align*}
    iK_1=- \begin{bmatrix}
        0 & 1 & 0 & 0\\
        1 & 0 & 0 & 0\\
        0 & 0 & 0 & 0\\
        0 & 0 & 0 & 0
    \end{bmatrix}, \quad
    iK_2=- \begin{bmatrix}
        0 & 0 & 1 & 0\\
        0 & 0 & 0 & 0\\
        1 & 0 & 0 & 0\\
        0 & 0 & 0 & 0
    \end{bmatrix}, \quad
    iK_3=- \begin{bmatrix}
        0 & 0 & 0 & 1\\
        0 & 0 & 0 & 0\\
        0 & 0 & 0 & 0\\
        1 & 0 & 0 & 0
    \end{bmatrix},
\end{align*}
thus we have (using $\mathbf n^2=n_x^2+n_y^2+n_z^2=1$)
\begin{align*}
    i \mathbf{n}\cdot\mathbf{K} &= -\begin{bmatrix}
        0 & n_x & n_y & n_z \\
        n_x & 0 & 0 & 0 \\
        n_y & 0 & 0 & 0 \\
        n_z & 0 & 0 & 0
    \end{bmatrix}, 
    \quad 
    (i \mathbf{n} \cdot \mathbf{K})^2 = \begin{bmatrix}
        1 & 0 & 0 & 0\\
        0 & n_x^2 & n_xn_y & n_xn_z \\
        0 & n_xn_y & n_y^2 & n_yn_z \\
        0 & n_xn_z & n_yn_z & n_z^2
    \end{bmatrix}
    \\
    (i \mathbf{n} \cdot \mathbf{K})^3 &= - \begin{bmatrix}
        0 & n_x & n_y & n_z \\
        n_x & 0 & 0 & 0 \\
        n_y & 0 & 0 & 0 \\
        n_z & 0 & 0 & 0
    \end{bmatrix} = \mathbf{n}\cdot\mathbf{K}.
\end{align*}
We see that $(i \mathbf{n}\cdot\mathbf{K})^{2k+1}= i \mathbf{n}\cdot\mathbf{K}$ and $(i \mathbf{n}\cdot\mathbf{K})^{2k}=(i \mathbf{n}\cdot\mathbf{K})^2$. Using this we find (setting $\omega^{00}=\omega^{ij}=0$ and $\omega^{i0}=-\omega^{0i}=n^i \eta$)
\begin{align*}
    B(\eta,\mathbf{n}) &= \exp(\frac{i}{2}\omega^{\rho\sigma}M_{\rho\sigma})
    \\
    &= \exp (\eta (i \mathbf{n}\cdot\mathbf{K}) )
    \\
    &= I+\eta(i\mathbf{n}\cdot\mathbf{K})+\frac{1}{2}\eta^2(i\mathbf{n}\cdot\mathbf{K})^2+\cdots
    \\
    &= I+\frac{1}{2}\eta^2(i \mathbf{n}\cdot\mathbf{K})^2+\frac{1}{4!}\eta^4(i\mathbf{n}\cdot\mathbf{K})^4+\cdots
    \\ &\qquad +\eta(i\mathbf{n}\cdot\mathbf{K})+\frac{1}{3!}\eta^3(i\mathbf{n}\cdot\mathbf{K})^3+\cdots
    \\
    &= I + \left(\frac{1}{2}\eta^2+\frac{1}{4!}\eta^4+\cdots\right)(i\mathbf{n}\cdot\mathbf{K})^2+\left(\eta+\frac{1}{3!}\eta^3+\cdots\right)(i\mathbf{n}\cdot\mathbf{K})
    \\
    &= I + (\cosh\eta-1)(i\mathbf{n}\cdot\mathbf{K})^2+\sinh\eta (i\mathbf{n}\cdot\mathbf{K})
    \\
    &= I - (\cosh\eta-1)(\mathbf{n}\cdot\mathbf{K})^2+i\sinh\eta(\mathbf{n}\cdot\mathbf{K}),
\end{align*}
which is the expression requested. As a consistency check, setting $\mathbf{n}=\mathbf{e_x}$ gives the result from Ex.~\ref{ex:Lorentz_explicit_x}:
\begin{align*}
    B(\eta,\mathbf{e_x})&=I+(\cosh\eta-1)(iK_1)^2+\sinh\eta(iK_1)
    \\
    &= I+(\cosh\eta-1)\begin{bmatrix}
        1&0&0&0 \\ 0&1&0&0 \\ 0&0&0&0 \\ 0&0&0&0
    \end{bmatrix} -\sinh\eta \begin{bmatrix}
        0&1&0&0 \\ 1&0&0&0 \\ 0&0&0&0 \\ 0&0&0&0
    \end{bmatrix}.
\end{align*}

\end{Answer}

### 2025-10-30 superspace.tex
Fixes for lecture 30.10.25

@@

>>>>

\begin{Answer}
Målsetningen her er å finne komponentfelt-transformasjonen til et vektorsuperfelt under en superjustér-transformasjon. For kompletthet, starter vi også med å minne om hvordan skalare superfelt transformerer under superjustér-transformasjoner.
\begin{equation*}
    \Phi_i \to \Phi_i' = e^{i q_i \Lambda}\Phi_i,
\end{equation*}
hvor $q_i$ er superfeltets ladning. En justér-transformasjon endrer ikke feltets superpoincaré-egenskaper, så det transformerte feltet bør også være venstrehendt.
\begin{align*}
    \bar{D}_{\dot{A}}\Phi_i \to \bar{D}_{\dot{A}}\Phi_i' = \bar{D}_{\dot{A}}\left[e^{i q_i \Lambda}\Phi_i\right] = e^{iq_i \Lambda}\underbrace{\bar{D}_{\dot{A}}\Phi_i}_{=0} + iq_i\left(\bar{D}_{\dot{A}}\Lambda\right)e^{i q_i \Lambda}\Phi_i \overset{(!)}{=} 0.
\end{align*}
Den siste likheten holder kun dersom $\bar{D}_{\dot{A}}\Lambda = 0$, altså oppfører $\Lambda$ seg som et venstrehendt skalart superfelt. For et høyrehendt skalart superfelt, $\Phi_i$, har vi 
\begin{align*}
    D_A \Phi_i^\dagger \to D_A \left(e^{i p_i \Lambda}\Phi_i\right)^\dagger = \big(\underbrace{D_A \Phi_i^\dagger}_{=0}\big)e^{-i p_i \Lambda^\dagger} - i p_i \Phi_i^\dagger\left(D_A \Lambda^\dagger\right)e^{- i p_i \Lambda^\dagger} \overset{(!)}{=} 0,
\end{align*}
som igjen krever at $D_A\Lambda^\dagger = 0$, altså er $\Lambda^\dagger$ et høyrehendt skalart superfelt.
Definisjonen av en abelsk superjustér-transformasjon for et vektor-superfelt er 
\begin{equation*}
    V \to V' = V - i \left[\Lambda - \Lambda^\dagger\right].
\end{equation*}
Parameter $\Lambda$ er igjen et skalart superfelt. Vi minner om formen på et vektorsuperfelt,
\begin{equation}
    \begin{aligned}
        \Phi(x, \theta, \bar{\theta}) &= C(x) + \theta^{A}\chi_A(x) + \bar{\theta}_{\dot{A}}\bar{\chi}^{\dot{A}}(x) + \theta \theta M(x) + \bar{\theta}\bar{\theta}M^*(x) \\
        & \quad + (\theta \sigma^\mu \bar{\theta})V_{\mu}(x) + \theta \theta \bar{\theta}_{\dot{A}}\bar{\lambda}^{\dot{A}}(x) + \bar{\theta}\bar{\theta}\theta^A\lambda_{A}(x) + \theta\theta \bar{\theta}\bar{\theta}D(x),
    \end{aligned}
    \label{vektorsuperfelt2}
\end{equation}
hvor vi har gitt komponentfeltene nye navn for ikke å ha navnekollisjon med skalarfeltene. Vi minner også om venstre- og høyrehendt-skalarfeltene, med samme navnekonvensjon som i forelesningsnotatene\footnote{Legge til en lenke her!}. Merk at i forhold til likning \eqref{venstrehendt skalart superfelt eksplisitt}, så er 
\begin{align}
    \label{venstrehendt skalarfelt2} 
    \Phi & =A(x) + i(\theta\sigma^\mu\bar{\theta})\partial_\mu A(x) - \frac{1}{4}\theta\theta\bar{\theta}\bar{\theta}\partial_\mu\partial^{\mu}A(x) + \sqrt{2}\theta^A\psi_{A}(x) - \frac{i}{\sqrt{2}}\theta\theta (\sigma^\mu\bar\theta)^A\partial_\mu \psi_A (x) + \theta \theta F(x)\\
    \label{høyrehendt skalarfelt2}
    \Phi^\dagger &= A^*(x) - i(\theta \sigma^{\mu}\bar{\theta})\partial_\mu A^*(x) - \frac{1}{4}\theta\theta\bar{\theta}\bar{\theta}\partial_\mu\partial^\mu A^*(x) + \sqrt{2}\bar{\theta}_{\dot{A}}\bar{\psi}^{\dot{A}}(x) + \frac{i}{\sqrt{2}}\bar{\theta} \bar{\theta}(\theta\sigma^{\mu})_{\dot{A}}\partial_\mu\bar{\psi}^{\dot{A}}(x) + \bar{\theta}\bar{\theta}F^*(x).
\end{align}

Vi kan for eksempel bruke at $\Lambda = i \Phi$, og likningene \eqref{vektorsuperfelt2}, \eqref{venstrehendt skalarfelt2} og  \eqref{høyrehendt skalarfelt2}
\begin{align}
    V \to V' &= V - i \left[\Lambda - \Lambda^\dagger \right] = V - i\Lambda - (i\Lambda)^\dagger \nonumber\\
   [\Lambda = i\Phi]\quad \quad  &= V + \Phi + \Phi^\dagger \nonumber \\
   [\eqref{vektorsuperfelt2}] \quad \quad &=
   C + \theta^{A}\chi_A + \bar{\theta}_{\dot{A}}\bar{\chi}^{\dot{A}} + \theta \theta M + \bar{\theta}\bar{\theta}M^* + (\theta \sigma^\mu \bar{\theta})V_{\mu} + \theta \theta \bar{\theta}_{\dot{A}}\bar{\lambda}^{\dot{A}} + \bar{\theta}\bar{\theta}\theta^A\lambda_{A} + \theta\theta \bar{\theta}\bar{\theta}D \nonumber \\
    [\eqref{venstrehendt skalarfelt2}] \quad \quad     & \quad \, +A + i(\theta\sigma^\mu\bar{\theta})\partial_\mu A - \frac{1}{4}\theta\theta\bar{\theta}\bar{\theta}\partial_\mu\partial^{\mu}A + \sqrt{2}\theta^A\psi_{A} + \frac{i}{\sqrt{2}}\theta\theta (\sigma^\mu\bar\theta)^A\partial_\mu \psi_A + \theta \theta F \nonumber \\
    [\eqref{høyrehendt skalarfelt2}] \quad \quad    & \quad \, +A^* - i(\theta \sigma^{\mu}\bar{\theta})\partial_\mu A^* - \frac{1}{4}\theta\theta\bar{\theta}\bar{\theta}\partial_\mu\partial^\mu A^* + \sqrt{2}\bar{\theta}_{\dot{A}}\bar{\psi}^{\dot{A}} + \frac{i}{\sqrt{2}}\bar{\theta} \bar{\theta}(\theta\sigma^{\mu})_{\dot{A}}\partial_\mu\bar{\psi}^{\dot{A}} + \bar{\theta}\bar{\theta}F^* \nonumber \\
    &= C + A^* + A + \theta^A( \chi_A + \sqrt{2}\psi_A) + \bar{\theta}_{\dot{A}}(\bar{\chi}^{\dot{A}} + \sqrt{2}\bar{\psi}^{\dot{A}}) + \theta \theta (M + F) + \bar{\theta}\bar{\theta}(M^* + F^*) \nonumber \\
    &\quad \, + (\theta \sigma^\mu \bar{\theta})[V_\mu + i \partial_\mu(A - A^*)] + \theta \theta \bar{\theta}_{\dot{A}}\left( \bar{\lambda}^{\dot{A}} + \frac{i}{\sqrt{2}}\sigma^{\mu B}_{\:\:\,\dot{A}}\partial_\mu \psi_B\right) + \bar{\theta}\bar{\theta}\theta^{A}\left(\lambda_A + \frac{i}{\sqrt{2}}\sigma^{\mu}_{A\dot{B}}\partial_\mu\bar{\psi}^{\dot{B}}\right) \nonumber \\
    & \quad \, + \theta \theta \bar{\theta}\bar{\theta}\left(D -  \frac{1}{4}\partial_\mu \partial^\mu[A + A^*]\right) 
    \label{superjustér-vektortrafo}\\
    &= C' + \theta^A \chi_A' + \bar{\theta}_{\dot{A}}\bar{\chi}_{\dot{A}}' + \theta \theta M' + \bar{\theta}\bar{\theta}M'^* + (\theta \sigma^\mu \bar{\theta})V_{\mu}' + \theta \theta \bar{\theta}_{\dot{A}}\bar{\lambda}'^{\dot{A}} + \bar{\theta}\bar{\theta}\theta^A\lambda_{A}' + \theta\theta \bar{\theta}\bar{\theta}D'.\nonumber
\end{align}
I siste linje har vi skrevet opp de transformerte komponentfeltene, og ved å sammenlikne med linjen over, kan vi lese ut hvordan komponentfeltene transformerer under en superjustér-transformasjon. Vi legger merke til at $\Box[A + A^*]$ dukker opp sammen med $D$-feltet, og at $[A + A^*]$ dukker opp sammen med $C$-feltet. Ved å redefinere $D \to D - \frac{1}{4}\Box C$, ser vi at den siste termen etter superjustèr-transformasjonen tar formen 
\begin{align*}
    \theta \theta \bar{\theta}\bar{\theta}D' = \theta \theta \bar{\theta}\bar{\theta}\left(D -  \frac{1}{4}\Box[A + A^*]\right) \xrightarrow[D \to D - \frac{1}{4}\Box C]{\text{redefinisjon}}\, & \theta \theta \bar{\theta}\bar{\theta}\left(D - \frac{1}{4}\Box C - \frac{1}{4}\Box[A + A^*]\right) \\
    =\, & \theta \theta \bar{\theta}\bar{\theta}\left(D -  \frac{1}{4}\Box[C + A + A^*]\right) = \theta \theta \bar{\theta}\bar{\theta}(D' + C').
\end{align*}
Vi kan gjøre det samme med $\lambda$. La $\lambda_A \to \lambda_A + \frac{i}{2}\sigma^\mu_{A\dot{B}}\partial_\mu \bar{\chi}^{\dot{B}}$. Dette er motivert av at vi ser at $\chi_A' = \chi_A + \sqrt{2}\psi_A$. Vi tar utregningen for $\lambda$, og så vet vi at det samme holder for $\bar{\lambda} = \lambda^\dagger$.
\begin{align*}
    \bar{\theta}\bar{\theta}\theta^{A}\lambda_A' = \bar{\theta}\bar{\theta}\theta^{A}\left(\lambda_A + \frac{i}{\sqrt{2}}\sigma^\mu_{A\dot{B}}\partial_\mu \bar{\psi}^{\dot{B}}\right) \xrightarrow[\lambda_A \to \lambda_A + \tfrac{i}{2}\sigma^\mu_{A\dot{B}}\bar{\chi}^{\dot{B}}]{\text{redefinisjon}} 
    & \, \bar{\theta}\bar{\theta}\theta^A\left(\lambda_A + \frac{i}{2}\sigma^\mu_{A\dot{B}}\partial_\mu\left[\bar{\chi}^{\dot{B}} + \sqrt{2} \bar{\psi}^{\dot{B}}\right]\right) \\
    =&\, \bar{\theta}\bar{\theta}\theta^A(\lambda_A' + \frac{i}{2}\sigma^\mu_{A\dot{B}}\partial_\mu \bar{\chi}'^{\dot{B}}).
\end{align*}
Med disse to redefinisjonene, ser vi at hverken $D$ eller $\lambda$ transformerer under superjustér-transformasjon. De andre feltene kan vi lese ut av likning \eqref{superjustér-vektortrafo}. Sammenfattet har vi 
\begin{align*}
    C &\to C' = C + A + A^* \\
    \chi_A &\to \chi_A' = \chi_A + \sqrt{2}\psi_A \\
    M & \to M' = M + F \\
    V_\mu &\to V_\mu' = V_\mu + i \partial_\mu(A - A^*)\\
    \lambda_A &\to \lambda_A' = \lambda_A   \quad \quad [\text{Ingen transformasjon}] \\
    D &\to D' = D \quad \quad \, \,\,[\text{Ingen transformasjon}]
\end{align*}
\end{Answer}

@@

\begin{Answer}
The Wess--Zumino gauge is  defined by the component field relations
\begin{align*}
    A + A^* &= -C, \\
    \psi & = -\frac{1}{\sqrt{2}}\chi, \\
    F &= -M.
\end{align*}
This gauge choice removes many terms from the vector superfield. Inserting into Eq.~\eqref{superjustér-vektortrafo}, we find
\begin{align}
    V \xrightarrow[\text{gauge}]{\text{Wess--Zumino}} V_{\text{WZ}} = (\theta \sigma^\mu \bar{\theta})\left[V_\mu + i\partial_\mu(A - A^*)\right] + \bar{\theta}\bar{\theta}\theta^{A}\lambda_A + \theta \theta \bar{\theta}_{\dot{A}}\bar{\lambda}^{\dot{A}} + \theta \theta \bar{\theta}\bar{\theta}D.
\end{align}
Here, all component fields have at least two factors of $\theta$. This is neat, because then $V_{\text{WZ}}^n = 0$ for all $n > 2$. We then calculate $V^2_{\text{WZ}}$. We notice that all terms, except the first, has three $\theta$ or $\bar{\theta}$ factors, and will not survive the squaring. Thus,
\begin{align*}
    V_{\text{WZ}}^2 &\, \,\,\,= (\theta\sigma^\mu\bar{\theta})[V_\mu + i\partial_\mu (A - A^*)](\theta\sigma^\nu \bar{\theta})[V_\nu + i\partial_\nu (A - A^*)] \\
    &\overset{\eqref{theta-sigma-theta-bar-kvadrat}}{=} \frac{1}{2}\theta \theta \bar{\theta}\bar{\theta}[V_\mu V^\mu + i\partial_\mu(A - A^*)V^\mu + V_\mu i \partial_\mu(A - A^*)-\partial_\mu(A - A^*)\partial^\mu(A - A^*)].
\end{align*}
This gives the following compact expression for the exponential of $V_{\text{WZ}}$,
\begin{align}
    e^{V_{\text{WZ}}} &= 1 + V_{\text{WZ}} + \frac{1}{2}V_{\text{WZ}}^2 \nonumber \\
    &= 1 + (\theta \sigma^\mu \bar{\theta})\left[V_\mu + i\partial_\mu(A - A^*)\right] + \bar{\theta}\bar{\theta}\theta^{A}\lambda_A + \theta \theta \bar{\theta}_{\dot{A}}\bar{\lambda}^{\dot{A}} \nonumber \\
    & \quad \,+ \frac{1}{4}\theta \theta \bar{\theta}\bar{\theta}\left[4D + V_\mu V^{\mu} + 2iV_\mu\partial^{\mu}(A - A^*) - \partial_\mu(A - A^*)\partial^{\mu}(A - A^*) \right].
    \label{Eksponensial, Wess-Zumino}
\end{align}
\end{Answer}
